Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-04-22 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
VSTTE 2020 paper update

All the equations above model the continuous-time behavior of the PV system; they produce real numbers except for the batteries and panels, where real numbers must be converted into integer ones, considering the minimum or maximum according to each equation. The verification and simulation tools need to handle non-linear real arithmetic to produce the correct result.

@@

Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries and inverters (lines $5$ to $8$). This procedure ensures that our synthesis engine checks all combinations of items from each equipment, and combines them to assemble a viable (candidate) PV solution, which meets user requirements.

@@

%---------------------------------------------------------------------------
\subsection{Optimization/Simulation Tools and Assumptions}
%---------------------------------------------------------------------------
Concerning the off-the-shelf optimization/simulation tools, only HOMER Pro performs an off-grid system with battery backup analysis and includes economical analysis. Here we used HOMER Pro version $3.13.1$ as a state-of-the-art simulation tool for comparison purposes. In particular, HOMER Pro has the following characteristics:
(a) it is available only for MS-Windows, its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; 
(b) it has two optimization algorithms: one algorithm simulates all of the feasible system configurations defined by the search space, and additionally, a proprietary derivative-free algorithm to search for the least-costly system;
(c) it does not have LCC cost in its reports, only Net Present Cost (NPC); however, we can obtain LCC from NPC; 
(d) the optimization analysis defines a load curve and temperature according to data collected from online databases. However, to allow a correct comparison, the curve load and the temperature were defined the same as our synthesis approach; 
(e) it does not have a charge controller. During the tests, we have chosen the ``load-following'' option, which produces enough power to meet the demand~\cite{HOMER} and (usually) presents a non-overestimated solution; 
(f) it was assumed 95\% availability of the PV system. By definition, ``availability'' is the percentage of time at which a power system can feed the load requirements~\cite{Khatib2014}. For an ordinary house electrical load, 95\% is considered acceptable;
(g) it was assumed a string of two batteries to match the voltage of the system of $24$ V DC, which was used for our automated synthesis tool; 
(h) it was included a generic flat-plate PV of $1$ kW and generic lead-acid batteries of $1$ kW ($83.4$ Ah capacity). During run-time, HOMER decides the size in kW of each based on feasibility and lower cost.

PVsyst is a PC software package developed by a Swiss company used globally for the study, sizing, simulation and data analysis of complete solar PV System. Contains: design, sizing, 3D shading scene, simulation, grid and off-grid features for PV systems. It uses world wide irradiation data from Meteonorm\footnote{https://meteonorm.com/en/}, and ageing analysis (PV system over the years). However, it does not performs optimization. Therefore, in this paper, PVsyst will be used to validate the optimal sizing obtained from the proposed technique and from the HOMER Pro.

@@

All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with $2.90$ GHz and $64$ GB RAM, running Ubuntu $16.04$ LTS $64$-bits. For HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores) with $1.7$ GHz and $4$ GB RAM running Windows 10. The hardware platform was not the same because of the availability of the machines; this has an impact on performance, which is less favorable to HOMER Pro. We perform the experiments with a predefined time out of $240$ minutes.

@@

\begin{table}
\caption{Case studies and results: optimization of stand-alone PV systems.}\label{tab1}
\begin{scriptsize}
\begin{tabular}{c|c|c|c|c}
\hline
\hline
Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)}& \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)}& \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& HOMER Pro 3.13.1\\
\hline
\hline
Specification & Result & Result & Result & Result \\
\hline
\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & OM & \makecell{SAT (620 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/48V\\LCC: US\$ 10,214.04} & \makecell{SAT (548 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/1600W/48V\\LCC: US\$ 10,214.04} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
\hline
\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & OM & TO & TO & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
\hline
\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & \makecell{SAT (63 min) \\NTP:14$\times$150W (7P-2S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 35A/145V\\Inverter 1,200W/48V\\LCC: US\$ 9,274.07} & TO & Not possible \\
\hline
\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & \makecell{SAT (147 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{SAT (605 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
\hline
\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & \makecell {SAT (36.70 min) \\NTP:4$\times$330W (2S-2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70}  & \makecell {SAT (254.25 min) \\NTP:4$\times$330W (2S-2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
\hline
\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & \makecell {SAT (380.93 min) \\NTP:6$\times$320W (2P-3S)\\NBT:18$\times$105Ah (2S-9P)\\Controller 35A/145V\\Inverter 400W/24V \\LCC: US\$ 10,136.61} & TO & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
\hline
\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & UNSAT (0.48 min) & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
\hline
\hline
\end{tabular}
\\Legend: OM = out of memory; TO = time out; IF = internal failure, E = energy.
\end{scriptsize}
\end{table}

@@

CPAchecker was able to synthesize optimal sizing in three out of the seven case studies (cases $1$, $4$, and $5$): the result was produced within the time limit, which varied from $254.25$ to $548$ minutes. Fig.~\ref{fig:CPAoptc1} illustrates the result of case $5$ with the optimal sizing appearing on the left size as the integer $3$ for the solar panel (which is the Canadian CS6U-330P model of $330$ W from the manufacturer Victron Energy), battery $0$ refers to the model 12MF80 of $80$ Ah from Moura, charge controller $0$ refers to the model 35A-145V MPPT from Victron  Energy, and the inverter number $2$ refers to the Epever model IP350-11 of $280$ W (nominal power) and $750$ W of surge power. The variables NTP, NPS, NPP, NPS, NBP, and NBTotal, also presented in the counterexample as well, shows the number of panels and batteries and how they are connected.

@@

Certain other HOMER Pro drawbacks were also noted:

\begin{itemize}
\item System equipment does not include an explicit charge controller . HOMER Pro includes a controller automatically just to simulate the charge/discharge of batteries and to meet the load requirement; however, without costs or even with electrical characteristics such as maximum current and voltage, which are common during PV sizing;
\item HOMER Pro requires the inclusion of some battery specification to initiate optimization; however, it does not change the electrical specifications during simulation; the results presented are multiples of the original battery type suggested by the user. For example, it was started with a $83.4$ Ah lead-acid battery and during simulation, HOMER Pro did not try to use other capacities or types;
\item HOMER Pro does not present the optimal solution in terms of connections of PV panel arrays, just the total in terms of power, i.e. it presents neither the models and the power of each PV panel nor the total of panels in series or parallel.
\end{itemize}

@@

Comparing the results of the formal synthesis with CPAchecker, and ESBMC, against those of  HOMER Pro, it was observed some distinct results, in terms of technical solution and cost (cf. Table~\ref{tab1}).  Related to performance there is a huge difference in favor of HOMER Pro that obtained the results in considerably less time: few seconds in opposite of an average of $234$ minutes for the automated synthesis technique.

@@

In one hand, related to the PV panels sizing, the results presented by the automated synthesis were smaller in terms of power than the produced by the simulation tool. The difference varied from $19$\% to $65$\%. In the other hand, related to the battery bank, the results were smaller in terms of capacity to the HOMER Pro. The difference was among $34$\% to $68$\%.

Those discrepancies are not easy to address without some real systems validation. The mathematical models are different and particular parameters can be tuned as well in each technique, and that can justify the difference, which was presented in all the case studies.

As a comparison, consider case study $5$: the optimal solution provided by HOMER Pro requires $17$\% more PV panels than the solution presented by the synthesis tool, and HOMER Pro does not show the arrangement of arrays (i.e. the number of series and parallel PV panels); the battery bank presented by HOMER Pro provides a capacity of $417$ Ah ($5 \times 83.4$ Ah), while the synthesis tool presented an optimal solution with a total capacity of $560$ Ah ($7 \times 80$ Ah) and this represent a difference of $34$\%.

Comparing the optimization results with those the real-world, the author had four PV systems deployed and monitored since June $2018$ in a riverside community in State pf Amazonas, Brazil, with demands  similar to those of case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries. These solutions are closer to the results from PV panel, controller and inverter presented by the proposed formal synthesis approach than that of HOMER Pro, thereby showing that the solution is sound, which answers \textit{EQ1}. However the solution presented for the battery bank is very different.

HOMER Pro suggests a value in kW for the inverters that is very close to the peak of every case study, and it is just a reference value and not a commercial value of the inverter employed. The proposed synthesis tool, however, presents inverters that are commercial and can be bought off-the-shelf. This is a clear advantage of the formal synthesis method.

@@

Summarizing, the synthesis tool is capable of presenting a solution which is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro. In particular, the automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from the manufacturer data sheet, including  the model of the component, nominal current and voltage. In this respect, even the name of the manufacturer can be cited (in Table~\ref{tab1} it was removed to avoid unauthorized advertising).

@@

Our novelty relies on a practical approach to pursuit the optimal solution of PV systems using contemporary formal methods. The use of formal synthesis to design PV systems has no precedent in literature; we show that the results of our approach, using seven case studies, are promising. Our synthesis tool can present a solution, which is far detailed and closer to the commercial reality than the solution presented by HOMER Pro, a state-of-the-art commercial tool. In particular, the battery autonomy feature, together with the details of every component of a PV system solution, is an advantage for our synthesis approach. These technical details are essential for the owner of the PV system since the industry demands proximity between the result presented by off-the-shelf optimization tools and the items of equipment for solar systems available on the market to achieve accuracy. Lastly, the use of data from real deployed systems in Amazonas State (Brazil) was essential to validate the comparison.

%Our novelty relies on a practical approach to pursuit the optimal solution of PV systems using contemporary formal methods. The use of formal synthesis to design PV systems has no precedent in literature; we show that the results of our approach, using seven case studies, are promising. Our synthesis tool can present a solution, which is far detailed and closer to the commercial reality than the solution presented by HOMER Pro, a state-of-the-art commercial tool. In particular, the battery autonomy feature together with the details of every component of a PV system solution are an advantage for our synthesis approach. These technical details are essential for the owner of the PV system since the industry demands proximity between the result presented by optimization tools and the items of equipment for solar systems available on the market; and not just maximum or minimum values of parameters given by off-the-shelf optimization tools, which still need to be adjusted according to the chosen equipment. Lastly, the use of data from real deployed systems in Amazonas State (Brazil) was essential to validate the comparison.

%and aid the process of equipment purchase 
%, e.g., complete electrical information from datasheet of manufacturers, including the component model, nominal current, and voltage,

%
% ---- Bibliography ----
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{trindadeThesis}
%
\end{document}
%\subsection{Design and Simulation of Solar PV systems}
%The design and validation of a PV system can be done by hand or with the aid of a software tool. In order to address different aspects of the PV system design, there are various software tools available in the literature~\cite{Rajanna,Rawat}.
%public domain and commercial software available for the PV market. 
%According to \cite{Brooks}, t
%%%%%%%%%%
%
%The capabilities of tools available in the literature range from simple solar resource and %energy production estimation, %to site survey and system design tools,
%to complex financial analysis and project optimization. At this study, the commercial simulation tool HOMER PRO was selected to be used at the case studies in order to be compared with the automated verification tools.

>>>>

All the equations above model the continuous-time behaviour of the PV system; they produce real numbers except for the batteries and panels, where real numbers must be converted into integer ones, considering the minimum or maximum according to each equation. The verification and simulation tools need to handle non-linear real arithmetic to produce the correct result.

@@

Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries and inverters (lines $5$ to $8$). This procedure ensures that our synthesis engine checks all combinations of items from each equipment, and combines them to assemble a viable (candidate) PV solution, which meets user requirements. A list of forty equipment from ten different manufacturers was provided (as INPUT) to our synthesis engine in order to allow the choice of every item of PV sizing. Data sheet from each item was necessary to collect technical information. Moreover, the price of each item was obtained from available quotations in the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars. All this data is available online\footnote{https://drive.google.com/file/d/1xZtAR4Wvgfqgox2PgySuPP-fZ9OA1u1j/view?usp=sharing}.

@@

%---------------------------------------------------------------------------
\subsection{Optimization/Simulation Tools and Assumptions}
%---------------------------------------------------------------------------
Concerning the off-the-shelf optimization/simulation tools, only HOMER Pro performs an off-grid system with battery backup analysis and includes economical analysis. Here we used HOMER Pro version $3.13.1$ as a state-of-the-art optimization tool for comparison purposes. In particular, HOMER Pro has the following characteristics:
(a) it is available only for MS-Windows, its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; 
(b) it has two optimization algorithms: one algorithm simulates all of the feasible system configurations defined by the search space, and additionally, a proprietary derivative-free algorithm to search for the least-costly system;
(c) it does not have LCC cost in its reports, only Net Present Cost (NPC); however, we can obtain LCC from NPC; 
(d) the optimization analysis defines a load curve and temperature according to data collected from online databases. However, to allow a correct comparison, the curve load and the temperature were defined the same as our synthesis approach; 
(e) it does not have a charge controller. During the tests, we have chosen the ``load-following'' option, which produces enough power to meet the demand~\cite{HOMER} and (usually) presents a non-overestimated solution; 
(f) it was assumed 95\% availability of the PV system. By definition, ``availability'' is the percentage of time at which a power system can feed the load requirements~\cite{Khatib2014}. For an ordinary house electrical load, 95\% is considered acceptable;
(g) it was assumed a string of two batteries to match the voltage of the system of $24$ V DC, which was used for our automated synthesis tool; 
(h) it was included a generic flat-plate PV of $1$ kW and generic lead-acid batteries of $1$ kW ($83.4$ Ah capacity). During run-time, HOMER decides the size in kW of each based on feasibility and lower cost.

In order to validate and compare the optimal sizing solution produced by our approach and by HOMER Pro, we use a complete simulation tool, called PVsyst version $6.86$, with plenty of commercial equipment in its data bank, in a comparison for a entire years weather data of simulation in order to guarantee that the proposed sizing meets the electrification requirements. PVsyst is a PC software package developed by a Swiss company used globally for the study, sizing, simulation and data analysis of solar PV systems. It contains: design, sizing, 3D shading scene, simulation, grid and off-grid features. It uses world wide irradiation data from Meteonorm\footnote{https://meteonorm.com/en/}, and ageing analysis. However, it does not performs optimization. Drawbacks of PVsyst: it does nor perform optimization therefore it needs the system sized in order to validated it, PVsyst does not have commercial inverter equipment and therefore does not consider surge power demand as the ones produced by air conditioners and refrigerators for few seconds. PVsyst is a paid software with $30$-day test possibility and runs only in MS-Windows operational system.

@@

All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with $2.90$ GHz and $64$ GB RAM, running Ubuntu $16.04$ LTS $64$-bits. For HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores) with $1.7$ GHz and $4$ GB RAM running Windows 10. The hardware platform was not the same because of the availability of the machines; this has an impact on performance, which is less favourable to HOMER Pro. PVsyst used the same configuration as HOMER Pro. We perform the experiments with a predefined time out of $660$ minutes.

@@

\begin{table}
\caption{Case studies and results: optimization of stand-alone PV systems.}\label{tab1}
\begin{scriptsize}
\begin{tabular}{c|c|c|c|c}
\hline
\hline
Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)}& \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)}& \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& HOMER Pro 3.13.1\\
\hline
\hline
Specification & Result & Result & Result & Result \\
\hline
\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & OM & \makecell{SAT (620 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/48V\\LCC: US\$ 10,214.04} & \makecell{SAT (548 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/1600W/48V\\LCC: US\$ 10,214.04} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
\hline
\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & OM & TO & TO & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
\hline
\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & \makecell{SAT (63 min) \\NTP:14$\times$150W (7P-2S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 35A/145V\\Inverter 1,200W/48V\\LCC: US\$ 9,274.07} & TO & Not possible \\
\hline
\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & \makecell{SAT (147 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{SAT (605 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
\hline
\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & \makecell {SAT (36.70 min) \\NTP:4$\times$330W (2S-2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70}  & \makecell {SAT (254.25 min) \\NTP:4$\times$330W (2S-2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
\hline
\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & \makecell {SAT (380.93 min) \\NTP:6$\times$320W (2P-3S)\\NBT:18$\times$105Ah (2S-9P)\\Controller 35A/145V\\Inverter 400W/24V \\LCC: US\$ 10,136.61} & TO & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
\hline
\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & UNSAT (0.48 min) & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
\hline
\hline
\end{tabular}
\\Legend: OM = out of memory; TO = time out; IF = internal failure; E = energy;        NTP = total number of panels, NBtotal = total number of batteries, NPS = number of panels in series; NPP = number of panels in parallel, NBS = number of batteries in series; NBP = number of batteries in parallel; LCC = Life Cycle Cost.
\end{scriptsize}
\end{table}

@@

CPAchecker was able to synthesize optimal sizing in three out of the seven case studies (cases $1$, $4$, and $5$): the result was produced within the time limit, which varied from $254.25$ to $548$ minutes. Fig.~\ref{fig:CPAoptc1} illustrates the result of case $5$ with the optimal sizing appearing on the left size as the integer $3$ for the solar panel (which is the Canadian CS6U-330P model of $330$ W from the manufacturer Victron Energy), battery $0$ refers to the model 12MF80 of $80$ Ah from Moura, charge controller $0$ refers to the model 35A-145V MPPT from Victron  Energy, and the inverter number $2$ refers to the Epever model IP350-11 of $280$ W (nominal power) and $750$ W of surge power. The variables NTP, NPS, NPP, NBS, NBP, and NBTotal, also presented in the counterexample as well, shows the number of panels and batteries and how they are connected.

@@

Certain other HOMER Pro drawbacks were also noted: (1) System equipment does not include an explicit charge controller . HOMER Pro includes a controller automatically just to simulate the charge/discharge of batteries and to meet the load requirement; however, without costs or even with electrical characteristics such as maximum current and voltage, which are common during PV sizing; (2) HOMER Pro requires the inclusion of some battery specification to initiate optimization; however, it does not change the electrical specifications during simulation; the results presented are multiples of the original battery type suggested by the user. For example, it was started with a $83.4$ Ah lead-acid battery and during simulation, HOMER Pro did not try to use other capacities or types; and (3) HOMER Pro does not present the optimal solution in terms of connections of PV panel arrays, just the total in terms of power, i.e. it presents neither the models and the power of each PV panel nor the total of panels in series or parallel.

@@

Comparing the results of the formal synthesis with CPAchecker, and ESBMC, against those of  HOMER Pro, it was observed some distinct results, in terms of technical solution and cost (cf. Table~\ref{tab1}).  Related to performance there is a huge difference in favour of HOMER Pro that obtained the results in considerably less time: few seconds in opposite of an average of $234$ minutes for the automated synthesis technique.

@@

In one hand, related to the PV panels sizing, the results presented by the automated synthesis were smaller in terms of power than the produced by the simulation tool. The difference varied from $19$\% to $65$\%. In the other hand, related to the battery bank, the results were smaller in terms of capacity to the HOMER Pro. The difference was among $34$\% to $68$\%. The mathematical models are different and particular parameters can be tuned as well in each technique, and that can justify the difference, which was presented in all the case studies.

Those discrepancies are not easy to address without some real systems validation. However we use the simulation software PVsyst in order to validate the optimal sizing produced. According PVsyst, we have to each case study:

\begin{itemize}
  	\item Case study 1: PVsyst indicates that a minimum necessary of $1,166$ W of PV panels and $381$ Ah of batteries. This is a case that was deployed at the field ($975$ W of panels and $440$ Ah of batteries), and simulation showed that the availability is lower than the $95$\% ($91.06$\% to be precise), therefore the sizing that was done "by hand" is not correct. Concerning our produced sizing, it was not found error during the 365-day of the year simulation, the same result for HOMER Pro. However the power values for panels and batteries show that HOMER Pro solution is oversized: $2.16$ times more for panels, and $1.31$ times more for batteries capability than necessary;
	\item Case study 2: PVsyst indicates that a minimum necessary of $1,482$ W of PV panels and $478$ Ah of batteries. This case has not field deployed to compare, and our approach did not produce solution. Only HOMER Pro left to comparison, however PVsyst showed that the sized PV system has $2.6$ times more panels and $1.74$ more batteries than the necessary;
	\item Case study 3: only our approach produced the optimal solution because there is the requirement of 12 hours of battery autonomy. HOMER Pro and PVsyst do not allow autonomy less than 24 hours;
	\item Case study 4: PVsyst indicates that a minimum necessary of $1,078$ W of PV panels and $354$ Ah of batteries. This one was deployed at the field ($975$ W of panels and $440$ ah of batteries), and PVsyst showed a not correct sizing because the system availability was only $87$\%. Concerning our optimal solution it was not found error, the same as HOMER Pro. However the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries capability than necessary;
	\item Case study 5: PVsyst indicates that a minimum necessary of $823$ W of PV panels and $268$ Ah of batteries. This one was deployed at the field, and PVsyst showed a correct sizing ($975$ W of panels and $440$ Ah of batteries). Concerning our optimal solution it was not found error, the same as HOMER Pro. However the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries capability than necessary;
	\item Case study 6:
	\item Case study 7:
\end{itemize}

%As a comparison, consider case study $5$: the optimal solution provided by HOMER Pro requires $17$\% more PV panels than the solution presented by the synthesis tool, and HOMER Pro does not show the arrangement of arrays (i.e. the number of series and parallel PV panels); the battery bank presented by HOMER Pro provides a capacity of $417$ Ah ($5 \times 83.4$ Ah), while the synthesis tool presented an optimal solution with a total capacity of $560$ Ah ($7 \times 80$ Ah) and this represent a difference of $34$\%.
%
Comparing the optimization results with those the real-world, the author had four PV systems deployed and monitored since June $2018$ in a riverside community in State pf Amazonas, Brazil, with demands  similar to those of case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries. These solutions are closer to the results from PV panel, controller and inverter presented by the proposed formal synthesis approach than that of HOMER Pro, thereby showing that the solution is sound, which answers \textit{EQ1}. However the solution presented for the battery bank is very different.

HOMER Pro suggests a value in kW for the inverters that is very close to the peak of every case study, and it is just a reference value and not a commercial value of the inverter employed. The proposed synthesis tool, however, presents inverters that are commercial and can be bought off-the-shelf, moreover consider surge power demand from the house that is not considered by HOMER Pro or PVsyst. This is a clear advantage of the formal synthesis method.

@@

Summarizing, our synthesis tool is capable of presenting a solution which is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro. In particular, the automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from the manufacturer data sheet, including  the model of the component, nominal current and voltage. In this respect, even the name of the manufacturer can be cited (in Table~\ref{tab1} it was removed to avoid unauthorized advertising). Moreover, the validation through PVsyst simulation, using the PV sizing produced by HOMER Pro and our synthesis approach, shows that our results are feasible and not as oversized as HOMER Pro results.

@@

Our novelty relies on a practical approach to pursuit the optimal solution of PV systems using contemporary formal methods. The use of formal synthesis to design PV systems has no precedent in literature; we show that the results of our approach, using seven case studies, are promising. Our synthesis tool can present a solution, which is far detailed and closer to the commercial reality than the solution presented by HOMER Pro, a state-of-the-art commercial tool. In particular, the battery autonomy feature, together with the details of every component of a PV system solution, is an advantage for our synthesis approach. These technical details are essential for the owner of the PV system since the industry demands proximity between the result presented by off-the-shelf optimization tools and the items of equipment for solar systems available on the market to achieve accuracy. It is worth mentioning that our synthesis technique was developed and uses open-source tools and environment, in contrast to the optimization and simulation tools used in this work. Lastly, the use of data from real deployed systems in Amazonas State (Brazil) and the validation through PVsyst was essential to validate the comparison.

%Our novelty relies on a practical approach to pursuit the optimal solution of PV systems using contemporary formal methods. The use of formal synthesis to design PV systems has no precedent in literature; we show that the results of our approach, using seven case studies, are promising. Our synthesis tool can present a solution, which is far detailed and closer to the commercial reality than the solution presented by HOMER Pro, a state-of-the-art commercial tool. In particular, the battery autonomy feature together with the details of every component of a PV system solution are an advantage for our synthesis approach. These technical details are essential for the owner of the PV system since the industry demands proximity between the result presented by optimization tools and the items of equipment for solar systems available on the market; and not just maximum or minimum values of parameters given by off-the-shelf optimization tools, which still need to be adjusted according to the chosen equipment. Lastly, the use of data from real deployed systems in Amazonas State (Brazil) was essential to validate the comparison.
%and aid the process of equipment purchase 
%, e.g., complete electrical information from datasheet of manufacturers, including the component model, nominal current, and voltage, 
%
% ---- Bibliography ----
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{trindadeThesis}
%
\end{document}
%\subsection{Design and Simulation of Solar PV systems}
%The design and validation of a PV system can be done by hand or with the aid of a software tool. In order to address different aspects of the PV system design, there are various software tools available in the literature~\cite{Rajanna,Rawat}.
%public domain and commercial software available for the PV market. 
%According to \cite{Brooks}, t
%%%%%%%%%%
%
%The capabilities of tools available in the literature range from simple solar resource and %energy production estimation, %to site survey and system design tools,
%to complex financial analysis and project optimization. At this study, the commercial simulation tool HOMER PRO was selected to be used at the case studies in order to be compared with the automated verification tools.
